---
title: "for loops"
author: "Tim Covino"
date: 
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dataRetrieval)

```

You could type out the sites and names or you could pull it from some whatNWISsites call. 

```{r}
sites <- c("06037500", "12363000")
names <- c("salmon", "flathead")
params <- c("00060", "00010") # This is temperature and Q. You can obviously change and then also change the readNWISdata to something else and the parameters, etc. 
start <- as_date("2020-10-01") # Just a nice round number for start time. 
end <- as_date("2021-09-30") #End of water year. 
service <- "dv" # Daily values

# Removed those sites for testing
# "12363000", "13296000", "12344000", "12447200", "13331500", "06191500"

```

Instead of writing a function, we use for(i in sites). So this will run through the list of sites and download the data and do whatever else you tell it. Then we create a filename that is data_, i. So it will write out data_06037500.csv for the first, data_12363000.csv for the second, so on. Then I just read the .csv in to check and make sure it worked.

```{r}
for (i in sites) {
  tmp <- readNWISdata(sites = i, parameterCd = params, service = service, startDate = start, endDate = end) %>% 
    renameNWISColumns()
  filename <- paste("data_", i, sep="")
  write_csv(tmp, file = paste("data/", filename, ".csv", sep=""))
}

test_df <- read_csv("data/data_06037500.csv")
```

Now we can add what is referred to as a "zipper" or "zippering" where we would name each file not by site but by name. See here: 

```{r}
for (k in seq_along(sites)) {
  tmp <- readNWISdata(
  sites = sites[k],
  parameterCd = params,
  service = service,
  startDate = start,
  endDate = end
  ) %>%
  renameNWISColumns()

filename <- paste0(names[k], ".csv")

write_csv(tmp, file = paste0("data/", filename))
rm(tmp)
}

```


We could also do this directly to the global environment. 

```{r}
for (k in seq_along(sites)) {
  tmp <- readNWISdata(
  sites = sites[k],
  parameterCd = params,
  service = service,
  startDate = start,
  endDate = end
  ) %>%
  renameNWISColumns()
  
assign(paste0(names[k]), tmp)
rm(tmp)
}
```


```{r}
list_of_files <- list.files(recursive = TRUE,
                            pattern = "\\.csv$",
                            full.names = FALSE)

df <- readr::read_csv(list_of_files, id = "file_name")
```

